Ionospheric Disturbances in Mexican Territory Produced by Objects Entering the Athmosphere from Space \tnoteref{tnote1}

### 2021-08-20 paper/manuscript.tex
Latest updates
- Few advances in paper
- Updated stations database
- Updated meteors database (removed event detected only by GLM-16)
- Updated vTEC maps to have the following improvements
  - Now we can choose the output format of maps between jpg, png and pdf
  - The colormap can be displayed in logarithmic scale
  - A second x axis in right hand graphs now display local time
  - The righthanded graphs now show shade in yellow when there is sunlight and cyan at night

    OXUM\hyperlink{Graham}{${}^3$} &  &  & 2021-03-31 & Cabral-Cano, Enrique, Salazar-Tlaczani, Luis, 2015, TLALOCNet - OXUM-oxum\_tnet\_mx2001 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5J964RP}.\\

@@

    UXAL\hyperlink{Graham}{${}^3$} &  &  & 2019-10-03 2020-01-15 2020-02-12 2020-04-08 2020-05-08 2020-12-19 2021-03-31 & Cabral-Cano, Enrique, Salazar-Tlaczani, Luis, 2015, TLALOCNet - UXAL-uxal\_tnet\_mx2005 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5DJ5D1C}.\\

>>>>

    OXUM\hyperlink{Graham}{${}^3$} & 15.66 & -96.50 & 2021-03-31 & Cabral-Cano, Enrique, Salazar-Tlaczani, Luis, 2015, TLALOCNet - OXUM-oxum\_tnet\_mx2001 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5J964RP}.\\

@@

    UXAL\hyperlink{Graham}{${}^3$} & 19.52 & -96.92 & 2019-10-03 2020-01-15 2020-02-12 2020-04-08 2020-05-08 2020-12-19 2021-03-31 & Cabral-Cano, Enrique, Salazar-Tlaczani, Luis, 2015, TLALOCNet - UXAL-uxal\_tnet\_mx2005 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5DJ5D1C}.\\
